Gravitational wave sources in our Galactic backyard: Predictions for BH and NS binaries in LISA

### 2021-07-01 paper/tex/sections/appendix.tex
remove old commented out strain stuff
move b_Z,i back to methods

% \section{Derivation of Strain and SNR Equations}\label{app:strain_snr_deriv}
% In this section we provide a full derivation/explanation of how we arrived at the equations used in our simulations.

% \subsection{Conversions and definitions}
% Each of these conversions and definitions are useful in the later derivations and we define them here for convenience. First, we define the chirp mass of a binary as 
% \begin{equation}\label{eq:chirpmass}
%     \mathcal{M}_c = \frac{(m_1 m_2)^{3/5}}{(m_1 + m_2)^{1/5}},
% \end{equation}
% where $m_1$ and $m_2$ are the primary and secondary mass of the binary. Kepler's third law is well known and allows one to convert between orbital frequency and the semi-major axis of a binary. For convenience we show it here
% \begin{equation}\label{eq:kepler3rd}
%     a = \qty(\frac{G(m_1 + m_2)}{(2 \pi f_{\rm orb})^{2}})^{1/3},\qquad f_{\rm orb} = \frac{1}{2 \pi} \sqrt{\frac{G(m_1 + m_2)}{a^3}}.
% \end{equation}
% As we deal with eccentric binaries, the different harmonic frequencies of gravitational wave emission become important. We therefore write that the relative power radiated into the $n^{\rm th}$ harmonic for a binary with eccentricity $e$ is \citep[][Eq.\,20]{Peters+1963}
% \begin{equation}\label{eq:g(n,e)}
%     \begin{aligned}
%         g(n, e) = \frac{n^{4}}{32} & \left\{ \left[ J_{n-2}(n e)-2 e J_{n-1}(n e)+\frac{2}{n} J_{n}(n e)+2 e J_{n+1}(n e)-J_{n+2}(n e)\right]^{2}\right.\\
%         &\left.+\left(1-e^{2}\right)\left[J_{n-2}(n e)-2 J_{n}(n e)+J_{n+2}(n e)\right]^{2}+\frac{4}{3 n^{2}}\left[J_{n}(n e)\right]^{2}\right\},
%     \end{aligned}
% \end{equation}
% where $J_{n}(v)$ is the Bessel function of the first kind. Thus, the sum of $g(n, e)$ over all harmonics gives the factor by which the gravitational wave emission is stronger for a binary of eccentricity $e$ over an otherwise identical circular binary. This enhancement factor is defined by Peters as \citep[][Eq.\,17]{Peters+1963}
% \begin{equation}\label{eq:eccentricity_enhancement_factor}
%     F(e) = \frac{1 + (73 / 24) e^2 + (37 / 96) e^4}{(1 - e^2)^{7/2}}.
% \end{equation}
% Note that $F(0) = 1$ as one would expect. A fun number to remember is that $F(0.5) \approx 5.0$, or in words, a binary with eccentricity $0.5$ loses energy to gravitational waves at a rate $5$ times higher than a similar circular binary.

% \subsection{Characteristic Strain}
% The characteristic strain from a binary in the $n^{\rm th}$ harmonic is defined as follows (e.g. \citealp[][Eq.\,56]{Barack+2004}; \citealp[][Eq.\,5.1]{ Flanagan+1998})
% \begin{equation}\label{eq:char_strain_dedf}
%     h_{c,n}^2 = \frac{1}{(\pi D_L)^2} \qty( \frac{2 G}{c^3} \frac{\dot{E_n}}{\dot{f_n}} ),
% \end{equation}
% where $D_L$ is the luminosity distance to the binary, $\dot{E}_n$ is the power radiated in the $n^{\rm th}$ harmonic and $\dot{f}_n$ is the rate of change of the $n^{\rm th}$ harmonic frequency. The power radiated in the $n^{\rm th}$ harmonic is given by \citep[][Eq. 19]{Peters+1963}
% \begin{equation}\label{eq:edot_peters}
%     \dot{E}_n = \frac{32}{5} \frac{G^{4}}{c^5} \frac{m_{1}^{2} m_{2}^{2}\left(m_{1}+m_{2}\right)}{a^{5}} g(n, e),
% \end{equation}
% where $m_1$ is the primary mass, $m_2$ is the secondary mass, $a$ is the semi-major axis of the binary and $e$ is the eccentricity. Using \eqref{eq:chirpmass} and \ref{eq:kepler3rd}, we can recast \eqref{eq:edot_peters} in a form more applicable for gravitational wave detections that is a function of only the chirp mass, orbital frequency and eccentricity.
% \begin{align}
%     \dot{E}_n &= \frac{32}{5} \frac{G^{4}}{c^5} \qty(m_{1}^{2} m_{2}^{2}\left(m_{1}+m_{2}\right)) g(n, e) \cdot \qty(\frac{(2 \pi f_{\rm orb})^{2}}{G(m_1 + m_2)})^{5/3} \\
%     \dot{E}_n &= \frac{32}{5} \frac{G^{7/3}}{c^5} \frac{m_{1}^{2} m_{2}^{2}}{\left(m_{1}+m_{2}\right)^{2/3}} (2 \pi f_{\rm orb})^{10/3} g(n, e) \\
%     \dot{E}_n(\mathcal{M}_c, f_{\rm orb}, e) &= \frac{32}{5} \frac{G^{7 / 3}}{c^{5}}\left(2 \pi f_{\mathrm{orb}} \mathcal{M}_{c}\right)^{10 / 3} g(n, e) \label{eq:edot}
% \end{align}
% The last term needed to define the characteristic strain in \eqref{eq:char_strain_dedf} is the rate of change of the $n^{\rm th}$ harmonic frequency. We can first apply the chain rule and note that
% \begin{equation}\label{eq:fdot_chainrule}
%     \dot{f}_{n} = \dv{f_{n}}{a} \dv{a}{t}.
% \end{equation}
% The frequency of the $n^{\rm th}$ harmonic is simply defined as $f_n = n \cdot f_{\rm orb}$ and therefore we can find an expression for $\dd{f_{n}} / \dd{a}$ by rearranging and differentiating \eqref{eq:kepler3rd}
% \begin{align}
%     f_{n} &= \frac{n}{2 \pi} \sqrt{\frac{G(m_1 + m_2)}{a^3}}, \\
%     \dv{f_{n}}{a} &= -\frac{3 n}{4 \pi} \frac{\sqrt{G(m_1 + m_2)}}{a^{5/2}}. \label{eq:dfda}
% \end{align}
% The rate at which the semi-major axis decreases is \citep[][Eq. 5.6]{Peters+1964}
% \begin{equation}\label{eq:dadt}
%     \dv{a}{t} = -\frac{64}{5} \frac{G^{3} m_{1} m_{2}\left(m_{1}+m_{2}\right)}{c^{5} a^{3}} F(e).
% \end{equation}
% Substituting \eqref{eq:dfda} and \ref{eq:dadt} into \eqref{eq:fdot_chainrule} gives an expression for $\dot{f}_{n}$
% \begin{align}
%     \dot{f}_n &= -\frac{3 n}{4 \pi} \frac{\sqrt{G(m_1 + m_2)}}{a^{5/2}} \cdot -\frac{64}{5} \frac{G^{3} m_{1} m_{2}\left(m_{1}+m_{2}\right)}{c^{5} a^{3}} F(e), \\
%     \dot{f}_n &= \frac{48 n}{5 \pi} \frac{G^{7/2}}{c^5} \qty(m_1 m_2 (m_1 + m_2)^{3/2}) \frac{F(e)}{a^{11/2}},
% \end{align}
% which, as above with $\dot{E}_n$, we can recast using Kepler's third law and the definition of the chirp mass
% \begin{align}
%     \dot{f}_n &= \frac{48 n}{5 \pi} \frac{G^{7/2}}{c^5} \qty(m_1 m_2 (m_1 + m_2)^{3/2}) F(e) \cdot \qty(\frac{(2 \pi f_{\rm orb})^{2}}{G(m_1 + m_2)})^{11/6}, \\
%     &= \frac{48 n}{5 \pi} \frac{G^{5/3}}{c^5} \frac{m_1 m_2}{(m_1 + m_2)^{1/3}} \cdot (2 \pi f_{\rm orb})^{11/3} \cdot F(e), \\
%     \dot{f}_n(\mathcal{M}_c, f_{\rm orb}, e) &= \frac{48 n}{5 \pi} \frac{\qty(G \mathcal{M}_c)^{5/3}}{c^5} (2 \pi f_{\rm orb})^{11/3} F(e) \label{eq:fdot}
% \end{align}
% With definitions of both $\dot{E}_n$ and $\dot{f}_n$, we are now in a position to find an expression for the characteristic strain by plugging \eqref{eq:edot} and \ref{eq:fdot} into \ref{eq:char_strain}:
% \begin{align}
%     h^2_{c,n} &= \frac{1}{(\pi D_L)^2} \qty( \frac{2 G}{c^3} \frac{\frac{32}{5} \frac{G^{7 / 3}}{c^{5}}\left(2 \pi f_{\mathrm{orb}} \mathcal{M}_{c}\right)^{10 / 3} g(n, e)}{\frac{48 n}{5 \pi} \frac{\qty(G \mathcal{M}_c)^{5/3}}{c^5} (2 \pi f_{\rm orb})^{11/3} F(e)} ) \\
%     &= \frac{1}{(\pi D_L)^2} \qty( \frac{2^{5/3} \pi^{2/3}}{3} \frac{(G \mathcal{M}_c)^{5/3}}{c^3} \frac{1}{f_{\rm orb}^{1/3}} \frac{g(n, e)}{n F(e)} ) \\
%     h_{c,n}^2(\mathcal{M}_c, D_L, f_{\rm orb}, e) &= \frac{2^{5/3}}{3 \pi^{4/3}} \frac{(G \mathcal{M}_c)^{5/3}}{c^3 D_L^2} \frac{1}{f_{\rm orb}^{1/3}} \frac{g(n, e)}{n F(e)} \label{eq:char_strain}
% \end{align}

% \subsection{Strain}
% The strain can be found by dividing the characteristic strain by the square root of twice the number of cycles. This is explained in \citet{Finn+2000} and in further detail in \citet{Moore+2015}. The physical reasoning behind the idea is that the binary will spend a certain amount of time in the vicinity of some frequency $f$ and cause a similar gravitational wave strain. This leads to the signal 'accumulating' and resulting in a larger signal-to-noise ratio. Therefore, the characteristic strain represents the strain measured by the detector over the duration of the mission, whilst the strain is what is emitted by the binary at each instantaneous moment.

% Following this logic, we can convert between characteristic strain and strain with \citep[e.g][see text before Eq.\,2.2]{Finn+2000}
% \begin{equation}\label{eq:strain-to-charstrain}
%     h_{c, n}^2 = \qty(\frac{2 f_n^2}{\dot{f}_n}) h_n^2.
% \end{equation}
% Therefore, using this, in addition to Eq. \ref{eq:fdot} and Eq. \ref{eq:char_strain}, we can write an expression for the strain amplitude of gravitational waves in the $n^{\rm th}$ harmonic
% \begin{align}
%     h_n^2 &= \qty(\frac{\dot{f}_n}{2 f_n^2}) h_{c, n}^2, \\
%     h_n^2 &= \qty(\frac{48 n}{5 \pi} \frac{\qty(G \mathcal{M}_c)^{5/3}}{c^5} (2 \pi f_{\rm orb})^{11/3} F(e) \cdot \frac{1}{2 n^2 f_{\rm orb}^2}) \qty(\frac{2^{5/3}}{3 \pi^{4/3}} \frac{(G \mathcal{M}_c)^{5/3}}{c^3 D_L^2} \frac{1}{n f_{\rm orb}^{1/3}} \frac{g(n, e)}{F(e)}), \\
%     h_n^2(\mathcal{M}_c, f_{\rm orb}, D_L, e) &= \frac{2^{25/3}}{5} \frac{(G \mathcal{M}_c)^{10/3}}{c^8 D_L^2} \frac{g(n, e)}{n^2} \qty(\pi f_{\rm orb})^{4/3} . \label{eq:strain}
% \end{align}

% \subsection{General Signal-to-Noise Ratio}
% We can start at the equation for the general signal-to-noise ratio from \citet{Flanagan+1998} (Eq. 2.30)
% \begin{equation}
%     \left\langle\rho^{2}\right\rangle=\frac{2(1+z)^{2}}{5 \pi^{2} D_L(z)^{2}} \int_{0}^{\infty} d f \frac{1}{f^{2} S_{n}(f)} \dv{E}{f}[(1 + z) f],
% \end{equation}
% where $z$ is the redshift. We need to adjust this equation in a couple of key ways for LISA Galactic binaries. First we multiply by 5 because of the way the signal response function is defined in LISA (converse to LIGO) -- \citet[see][]{Robson+2019} for a good explanation. Additionally we can set $z = 0$ for Galactic binaries, convert to SI units from geometric units (as is our convention in this document) and integrate over specific frequency limits.
% \begin{equation}\label{eq:snr_abs}
%     \avg{\rho_n^2} = \int_{f_{n, i}}^{f_{n, f}} \underbrace{\frac{2 G}{\pi^2 c^3 D_L^2} \dv{E_n}{f_n}}_{\text{signal}} \underbrace{\frac{1}{f_n^2 S_{\rm n}(f_n)}}_{\text{noise}} \dd{f_n}.
% \end{equation}
% It is now useful to inspect the `signal' term in the equation. We can do this specifically by first finding an expression for $\dd{E_n}/\dd{f_n}$ through the chain rule. We can write
% \begin{equation}\label{eq:dedf}
%     \dv{E_n}{f_n} = \dv{E_n}{t} \dv{a}{f_n} \dv{t}{a},
% \end{equation}
% where each term respectively comes from \eqref{eq:edot_peters}, the inverse of \eqref{eq:dfda} and the inverse of \eqref{eq:dadt}.
% We can substitute these into Eq. \ref{eq:dedf} and simplify as follows
% \begin{align}
%     \dv{E_n}{f_n} &= \frac{32}{5} \frac{G^{4}}{c^5} \frac{m_1^2 m_2^2 \qty(m_1 + m_2)}{a^5} g(n, e) \cdot -\frac{4 \pi}{3 n} \frac{a^{5/2}}{(G(m_1 + m_2))^{1/2}} \cdot -\frac{5}{64} \frac{c^5 a^3}{G^3 m_1 m_2 (m_1 + m_2)} \frac{1}{F(e)}, \\
%     &= \frac{2 \pi}{3} \frac{G^{1/2} m_1 m_2}{(m_1 + m_2)^{1/2}} \frac{g(n, e)}{n F(e)} \cdot a^{1/2}, \\
%     &= \frac{2 \pi}{3} \frac{G^{1/2} m_1 m_2}{(m_1 + m_2)^{1/2}} \frac{g(n, e)}{n F(e)} \cdot \qty(\frac{G(m_1 + m_2)}{(2 \pi f_{\rm orb})^2})^{1/6}, \\
%     &= \frac{2^{2/3} \pi^{2/3}}{3} \frac{G^{2/3} m_1 m_2}{(m_1 + m_2)^{1/3}} \frac{g(n, e)}{n F(e)} \cdot f_{\rm orb}^{-1/3}, \\
%     \dv{E_n}{f_n} &= \frac{2^{2/3} \pi^{2/3}}{3} G^{2/3} \mathcal{M}^{5/3} \frac{g(n, e)}{n F(e)} \cdot f_{\rm orb}^{-1/3}.
% \end{align}
% If we further multiply this by the prefactor in \eqref{eq:snr_abs}, we arrive at an expression for the `signal' portion of the equation, which notably is exactly the square of the characteristic strain (see \eqref{eq:char_strain}).
% \begin{equation}
%     \dv{E_n}{f_n} \frac{2 G}{\pi^2 c^3 D_L^2} = \frac{2^{5/3} }{3 \pi^{4/3}} \frac{(G \mathcal{M}_c)^{5/3}}{c^3 D_L^2} \frac{1}{n f_{\rm orb}^{1/3}} \frac{g(n, e)}{F(e)} = h_{c,n}^2.
% \end{equation}
% We can therefore write that the sky-averaged signal-to-noise ratio for a Galactic binary is
% \begin{equation}\label{eq:snr_general}
%     \boxed{ \rho^2 = \sum_{n=1}^{\infty}  \int_{f_{n, i}}^{f_{n, f}} \frac{h_{c, n}^2}{f_n^2 S_{\rm n}(f_n)} \dd{f_n}. }
% \end{equation}

% \subsection{Stationary Signal-to-Noise Ratio}
% For our sample, it was extremely useful to note that the vast majority of our binaries were stationary in frequency space on the timescale of a space-based observing mission. In this case, the start and end frequencies are only separated by a very small $\Delta f_n$ and so we can make the approximation that
% \begin{align}
%     \rho_n^2 &= \lim_{\Delta f \to 0} \int_{f_{n}}^{f_{n} + \Delta f_n} \frac{h_{c, n}^2}{f_n^2 S_n(f_n)} \dd{f_n}, \nonumber \\
%     &\approx \frac{\Delta f_n \cdot h_{c, n}^2}{f_n^2 S_n(f_n)}.
% \end{align}
% Moreover, we can immediately write that $\Delta f_n = \dot{f}_n \Delta T$, where we know that $\Delta T = T_{\rm obs}$, such that
% \begin{equation}
%     \rho_n^2 = \left(\frac{\dot{f}_n}{f_n^2} h_{c, n}^2 \right) \frac{T_{\rm obs}}{S_n(f_n)},
% \end{equation}
% where the term in parentheses can be replaced with $2 h_n^2$ using Equation \ref{eq:strain-to-charstrain}. This gives the final expression for the signal-to-noise ratio when the stationary approximation is applied (as shown in Equation \ref{eq:snr_stat})
% \begin{equation}
%     \rho_{\rm stat}^2 = \sum_{n=1}^{\infty} \frac{2 T_{\rm obs} h_n^2}{S_n(f_n)} .
% \end{equation}

\section{Population Synthesis}\label{app:pop_synth}
\subsection{Initial conditions}

Between 1 and 100 million massive binaries are simulated for 50 metallicities equally spaced in log space between $Z \in [0.0001, 0.022]$, where $Z$ is the mass fraction of heavy elements. More binaries are simulated for higher metallicities to account for the lower formation rate of DCOs. These bins span the allowed metallicity range for the original fitting formulae on which COMPAS is based \citep{Hurley+2000}. This is repeated for \nMinusOneModels{} physics variations (see Section \ref{sec:variation_assumptions}) and so in total over a billion binaries were simulated.

@@

For each metallicity $Z$, the simulations result in a sample of binaries, each with a set of parameters
\begin{equation}
    \mathbf{b}_{{Z, i}} = \{m_1, m_2, a_{\rm DCO}, e_{\rm DCO}, t_{\rm evolve}, t_{\rm inspiral}, w\},
\end{equation}
for $i = 1, 2, \dots, N_{\rm binary}$, where $m_1$ and $m_2$ are the primary and secondary masses, $a_{\rm DCO}$ and $e_{\rm DCO}$ are the semi-major axis and eccentricity at the moment of double compact object (DCO) formation, $t_{\rm evolve}$ is the time between the binary's zero-age main sequence and DCO formation, $t_{\rm inspiral}$ is the time between DCO formation (that is immediately after the second supernova in the system) and gravitational wave merger, $w$ is the adaptive importance sampling weight assigned by STROOPWAFEL \cite[][Eq.~7]{Broekgaarden+2019}. We sample from these sets of parameters when creating synthetic galaxies.

\subsection{Physical assumptions in our fiducial model}\label{sec:fiducial_physics}
In this section we briefly summarise the main physical assumptions in our fiducial model. For more details see \citet{Broekgaarden+2021}.

@@

\textit{Supernovae:} We draw the remnant masses and natal kick magnitudes from different distributions depending on the type of supernova that occurs. For stars undergoing a general core-collapse supernova, we use the \textit{delayed} supernova remnant mass prescription from \citet{Fryer+2012}. The \textit{delayed} prescription does not reproduce the neutron star black hole mass gap and we use this as our default as it has been shown to provide a better fit for observed populations of DCOs \citep[e.g.][]{Vigna-Gomez+2018}. We draw the natal kick magnitudes from a Maxwellian velocity distribution with a one-dimensional root-mean-square velocity dispersion of $\sigma_{\rm rms}^{\rm 1D} = 265 \unit{km}{s^{-1}}$ \citep{Lyne+1994, Hobbs+2005}.

We assume that stars with helium core masses between $1.6$--$2.25 \unit{M_{\odot}}$ \citep{Hurley+2002} experience electron-capture supernovae (ECSN) \citep{Nomoto+1984, Nomoto+1987, Ivanova+2008}. We set all remnant masses to $1.26 \unit{M_{\odot}}$ in this case as an approximation of the solution to Equation 8 of \citet{Timmes+1996}. For these supernovae, we set $\sigma_{\rm rms}^{\rm 1D} = 30 \unit{km}{s^{-1}}$ \citep[e.g.][]{Pfahl+2002, Podsiadlowski+2004}.

We assume that stars that undergo case BB mass transfer \citep{Dewi+2002} experience extreme stripping which leads to an ultra-stripped supernova \citep{Tauris+2013, Tauris+2015}. For these supernovae we calculate the remnant mass using the \citet{Fryer+2012} prescription and use $\sigma_{\rm rms}^{\rm 1D} = 30 \unit{km}{s^{-1}}$ (as with ECSN).

Stars with final helium core masses between $60$-$135 \unit{M_{\odot}}$ are presumed to undergo a pair-instability, or pulsational pair-instability supernova \citep[e.g.][]{Woosley+2007, Farmer+2019}. We follow the prescription from \citet{Marchant+2019} as implemented in \citep{Stevenson+2019} for these supernovae.

We assume that kicks are isotropic in the frame of the collapsing star. We adopt a maximum neutron star mass of $2.5 \unit{M_{\odot}}$ \citep[e.g.][]{Kalogera+1996, Fryer+2015, Margalit+2017} for the fiducial model and change the \citet{Fryer+2012} prescription accordingly.

@@

\begin{figure*}[h]
    \centering
    \includegraphics[width=\textwidth]{variations_cdf_1_3.pdf}
    \caption{Cumulative distribution functions for the black hole mass, neutron star mass, eccentricity during the LISA mission and merger time for each DCO type and physics variation. In colour we show the fiducial populations compared to changing the mass transfer efficiency $\beta$. We additionally show the other physics variations in the background in light grey.}
    \label{fig:variations_cdf_1_3}
\end{figure*}

\begin{figure*}[h]
    \centering
    \includegraphics[width=\textwidth]{variations_cdf_4_6.pdf}
    \caption{As Fig.~\ref{fig:variations_cdf_1_3}, except comparing the fiducial population with models using different values for $\alpha_{\rm CE}$ and changing the stability of case BB mass transfer.}
    \label{fig:variations_cdf_4_6}
\end{figure*}

\begin{figure*}[h]
    \centering
    \includegraphics[width=\textwidth]{variations_cdf_7_10.pdf}
    \caption{As Fig.~\ref{fig:variations_cdf_1_3}, except comparing the fiducial population with models changing the maximum neutron star mass, remnant mass prescription and survivability of common envelope events initiated by Hertzsprung gap donors.}
    \label{fig:variations_cdf_7_10}
\end{figure*}

\begin{figure*}[h]
    \centering
    \includegraphics[width=\textwidth]{variations_cdf_11_14.pdf}
    \caption{As Fig.~\ref{fig:variations_cdf_1_3}, except comparing the fiducial population with models changing the core-collapse supernova kick distributions and the presence of BH kicks and PISNs.}
    \label{fig:variations_cdf_11_14}
\end{figure*}

>>>>

\section{Population Synthesis}\label{app:pop_synth}

In this section we summarise the main assumptions and settings that we use when performing population synthesis for this work. For a more general overview of every setting see \citet{Broekgaarden+2021}.

\subsection{Initial conditions}

We simulate between 1 and 100 million massive binaries for 50 metallicities equally spaced in log space between $Z \in [0.0001, 0.022]$, where $Z$ is the mass fraction of heavy elements. We simulate more binaries for higher metallicities to account for the lower formation rate of DCOs. These metallicities span the allowed metallicity range for the original fitting formulae on which COMPAS is based \citep{Hurley+2000}. This is repeated for \nMinusOneModels{} physics variations (see Section \ref{sec:variation_assumptions}) and so in total over two billion binaries were simulated.

@@

\subsection{Physical assumptions in our fiducial model}\label{sec:fiducial_physics}

@@

\textit{Supernovae:} We draw the remnant masses and natal kick magnitudes from different distributions depending on the type of supernova that occurs. For stars undergoing a general core-collapse supernova, we use the \textit{delayed} supernova remnant mass prescription from \citet{Fryer+2012}. The \textit{delayed} prescription does not reproduce the neutron star black hole mass gap and we use this as our default as it has been shown to provide a better fit for observed populations of DCOs \citep[e.g.][]{Vigna-Gomez+2018}. We draw the natal kick magnitudes from a Maxwellian velocity distribution with a one-dimensional root-mean-square velocity dispersion of $\sigma_{\rm rms}^{\rm 1D} = 265 \unit{km}{s^{-1}}$ \citep{Lyne+1994, Hobbs+2005}. We assume that stars with helium core masses between $1.6$--$2.25 \unit{M_{\odot}}$ \citep{Hurley+2002} experience electron-capture supernovae (ECSN) \citep{Nomoto+1984, Nomoto+1987, Ivanova+2008}. We set all remnant masses to $1.26 \unit{M_{\odot}}$ in this case as an approximation of the solution to Equation 8 of \citet{Timmes+1996}. For these supernovae, we set $\sigma_{\rm rms}^{\rm 1D} = 30 \unit{km}{s^{-1}}$ \citep[e.g.][]{Pfahl+2002, Podsiadlowski+2004}. We assume that stars that undergo case BB mass transfer \citep{Dewi+2002} experience extreme stripping which leads to an ultra-stripped supernova \citep{Tauris+2013, Tauris+2015}. For these supernovae we calculate the remnant mass using the \citet{Fryer+2012} prescription and use $\sigma_{\rm rms}^{\rm 1D} = 30 \unit{km}{s^{-1}}$ (as with ECSN). Stars with final helium core masses between $35$-$135 \unit{M_{\odot}}$ are presumed to undergo a pair-instability, or pulsational pair-instability supernova \citep[e.g.][]{Woosley+2007, Farmer+2019}. We follow the prescription from \citet{Marchant+2019} as implemented in \citep{Stevenson+2019} for these supernovae. We assume that kicks are isotropic in the frame of the collapsing star. We adopt a maximum neutron star mass of $2.5 \unit{M_{\odot}}$ \citep[e.g.][]{Kalogera+1996, Fryer+2015, Margalit+2017} for the fiducial model and change the \citet{Fryer+2012} prescription accordingly.

@@

\begin{figure*}[htb]
    \centering
    \includegraphics[width=\textwidth]{variations_cdf_1_3.pdf}
    \caption{Cumulative distribution functions for the black hole mass, neutron star mass, eccentricity during the LISA mission and merger time for each DCO type and physics variation. In colour we show the fiducial populations compared to changing the mass transfer efficiency $\beta$. We additionally show the other physics variations in the background in light grey.}
    \label{fig:variations_cdf_1_3}
\end{figure*}

\begin{figure*}[p]
    \centering
    \includegraphics[width=\textwidth]{variations_cdf_4_6.pdf}
    \caption{As Fig.~\ref{fig:variations_cdf_1_3}, except comparing the fiducial population with models using different values for $\alpha_{\rm CE}$ and changing the stability of case BB mass transfer.}
    \label{fig:variations_cdf_4_6}
\end{figure*}

\begin{figure*}[p]
    \centering
    \includegraphics[width=\textwidth]{variations_cdf_7_10.pdf}
    \caption{As Fig.~\ref{fig:variations_cdf_1_3}, except comparing the fiducial population with models changing the maximum neutron star mass, remnant mass prescription and survivability of common envelope events initiated by Hertzsprung gap donors.}
    \label{fig:variations_cdf_7_10}
\end{figure*}

\begin{figure*}[p]
    \centering
    \includegraphics[width=\textwidth]{variations_cdf_11_14.pdf}
    \caption{As Fig.~\ref{fig:variations_cdf_1_3}, except comparing the fiducial population with models changing the core-collapse supernova kick distributions and the presence of BH kicks and PISNs.}
    \label{fig:variations_cdf_11_14}
\end{figure*}

### 2021-07-01 paper/tex/sections/methods.tex
move b_Z,i back to methods

>>>>

The result of the simulations is a sample of binaries, which, for each metallicity $Z$, have the parameters
\begin{equation}
    \mathbf{b}_{{Z, i}} = \{m_1, m_2, a_{\rm DCO}, e_{\rm DCO}, t_{\rm evolve}, t_{\rm inspiral}, w\},
\end{equation}
for $i = 1, 2, \dots, N_{\rm binary}$, where $m_1$ and $m_2$ are the primary and secondary masses, $a_{\rm DCO}$ and $e_{\rm DCO}$ are the semi-major axis and eccentricity at the moment of double compact object (DCO) formation, $t_{\rm evolve}$ is the time between the binary's zero-age main sequence and DCO formation, $t_{\rm inspiral}$ is the time between DCO formation (that is immediately after the second supernova in the system) and gravitational wave merger, $w$ is the adaptive importance sampling weight assigned by STROOPWAFEL \cite[][Eq.~7]{Broekgaarden+2019}. We sample from these sets of parameters when creating synthetic galaxies.
